Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-10-18 sections/correlated-sicm-and-fm.tex
Update correlated-sicm-and-fm.tex
Second typo-correction

In a study investigating the formation of human immunodeficiency virus-like
particles (VLPs) the correlated SICM-fluorescence confocal microscopy was used
to investigate topography changes together with the distribution of
fluorescently labeled viral proteins like Gag or Viral Protein R
\cite{Bednarska2020}. In contrast to investigating the virus formation with
TIRF microscopy \cite{Jouvenet2008}, the combination of SICM and confocal FM
allowed to investigate the apical side of the cells. It was found that the
release of VLPs is a lot faster than the release at the basal cell side as
known from TIRF investigations and furthermore, a potential impact on the
release time by the application of a fluorescent marker was found
\cite{Bednarska2020}.

@@

First, SSCM has been used for investigating the dynamics of the interaction of
Cy3-labeled polyoma virus-like particles (VLPs) with Cos-7 cells
\cite{Gorelik2002a}.

>>>>

In a study investigating the formation of human immunodeficiency virus-like
particles (VLPs) the correlated SICM-fluorescence confocal microscopy was used
to investigate topography changes together with the distribution of
fluorescently labelled viral proteins like Gag or Viral Protein R
\cite{Bednarska2020}. In contrast to investigating the virus formation with
TIRF microscopy \cite{Jouvenet2008}, the combination of SICM and confocal FM
allowed to investigate the apical side of the cells. It was found that the
release of VLPs is a lot faster than the release at the basal cell side as
known from TIRF investigations and furthermore, a potential impact on the
release time by the application of a fluorescent marker was found
\cite{Bednarska2020}.

@@

First, SSCM has been used for investigating the dynamics of the interaction of
Cy3-labelled polyoma virus-like particles (VLPs) with Cos-7 cells
\cite{Gorelik2002a}.
